\makeatletter
\renewcommand\@biblabel[1]{}
\makeatother

\renewcommand\bibname{Referencias}

\begin{thebibliography}{50}

\bibitem[Bersha, 2010]{Bersha}\sangriareferencias
Bersha K.~S. (2010), \emph{<<Spectral Imaging And Analysis Of Human Skin>>}. University of Eastern Finland.
\espacioreferencias
\bibitem[P\'{e}rez, 2012]{Perez}\sangriareferencias
P\'{e}rez A.~D. (2012), \emph{<<Estudio de la Reflexi\'{o}n \'{O}ptica Difusa en Tejido Biol\'{o}gico>>}. Escuela Superior de Ingenier\'{i}a Mec\'{a}nica y El\'{e}ctrica Unidad Zacatenco.
\espacioreferencias
\bibitem{HunterLab}\sangriareferencias
Hunter Associates Laboratory, \emph{<<HunterLab, The World's true measure of color>>}. http://www.hunterlab.com/about-us.html.
\espacioreferencias
\bibitem{HunterLab-manual}\sangriareferencias
Hunter Associates Laboratory (2001), \emph{<<Universal Software Versions 4.10 and Above User's Manual>>}. Reston, Virginia.
\espacioreferencias
\bibitem{MiniScanXEPlus-manual}\sangriareferencias
Hunter Associates Laboratory (2006), \emph{<<MiniScan XE Plus User's Guide Version 2.4>>}. Reston, Virginia.
\espacioreferencias
\bibitem[Sommerville, 2005]{Sommerville}\sangriareferencias
Sommerville I. (2005), \emph{<<Ingenier\'{i}a del Software>>}, 7ma~ed. Madrid, Espa\~{n}a: Pearson Education.
\espacioreferencias
\bibitem{CIE}\sangriareferencias
CIE, \emph{<<Commission Internationale de l'Eclairage, International Commission on Illumination>>}. http://www.cie.co.at/index.php.
\espacioreferencias
\bibitem[Schanda, 2007]{Schanda}\sangriareferencias
Schanda J. (2007), \emph{<<Colorimetry: understanding the CIE system>>}. Hoboken, Nueva Jersey: John Wiley \& Sons.
\espacioreferencias
\bibitem[Wagner et al., 2002]{Wagner}\sangriareferencias
Wagner J., Jovel C., Norton H., Parra E., Shriver M. (2002), \emph{<<Comparing Quantitative Measures of Erythema, Pigmentation and Skin Response using Reflectometry>>}. Pigment Cell Res.
\espacioreferencias
\bibitem[Narea et al., 2015]{Narea}\sangriareferencias
Narea F., Vivas S., Mu\~{n}oz A. (2015), \emph{<<Recuperaci\'{o}n del coeficiente de absorci\'{o}n de la epidermis en la piel humana>>}. Sociedad Espa\~{n}ola de \'{O}ptica.
\espacioreferencias
\bibitem[Baskerville, 1999]{Baskerville}\sangriareferencias
Baskerville R.~L. (1999), \emph{<<Investigating Information Systems with Action Research>>}, vol~2. Atlanta, GA: Association for Information Systems.
\espacioreferencias
\bibitem[Schwaber y Sutherland, 2013]{Schwaber&Sutherland}\sangriareferencias
Schwaber K., Sutherland J. (2013), \emph{<<The Definitive Guide to Scrum: The Rules of the Game>>}. http://www.scrumguides.org/.
\espacioreferencias
\bibitem[Hundermark, 2015]{Hundermark}\sangriareferencias
Hundermark P. (2015), \emph{<<Do Better SCRUM>>}, versi\'{o}n~3.\hskip 1em plus
  0.5em minus 0.4em\relax Agile42 - The Agile Coaching Company.
\espacioreferencias
\bibitem[Kroll y Kruchten, 2003]{Kroll&Kruchten}\sangriareferencias
Kroll P., Kruchten P. (2003), \emph{<<The Rational Unified Process Made Easy: A Practitioner's Guide to the RUP>>}. Addison-Wesley.
\espacioreferencias
\bibitem{RS232}\sangriareferencias
Magneto Tech Research, \emph{<<USB to Serial adapters Wiki>>}.\hskip 1em plus
0.5em minus 0.4em\relax http://www.usb-serial-adapter.org/.
\espacioreferencias
\bibitem{Qt}\sangriareferencias
The Qt Company, \emph{<<Qt, a Cross-Platform Framework for Application Development>>}. https://wiki.qt.io/About\_Qt.
\espacioreferencias
\bibitem{VS}\sangriareferencias
Microsoft, \emph{<<Visual Studio Community, a fully-featured, extensible IDE>>}. https://www.visualstudio.com/products/visual-studio-community-vs
\espacioreferencias
\bibitem{QCustomPlot}\sangriareferencias
QCustomPlot, \emph{<<A Qt C++ widget for plotting and data visualization>>}. http://www.qcustomplot.com/index.php/introduction.

\end{thebibliography}